### 2021-10-29 paper/output/document/paper41.tex
did goals

Notice that the antecedent specifies that the circumstances hold at the given world. 
When evaluating if a maxim is universalizable or not, we want to ignore worlds where the circumstance 
do not hold. At these worlds, the maxim is trivially effective and thus trivially universalizable. If we didn't exclude such worlds from 
consideration, a maxim with circumstances that ever fail to hold would be universalizable. Clearly 
this is not a desirable conclusion, since maxims like ``When you need money, lie to get easy money"
would be universalizable.%
}%
\begin{isamarkuptext}%
As before, the concepts of prohibition and permissibility will be helpful here. The unit of 
evaluation for my formalization of the FUL is the act of willing a maxim, which entails performing 
the maxim's act in the relevant circumstances. Therefore, I will say that, just as the act of willing a
 maxim can be obligatory for a subject, it can be prohibited or permissible for a subject.\footnote{In 
the rest of this section, for convenience, I will use the phrase ``subject s willing maxim M is obligatory" 
interchangeably with ``maxim M is obligatory for subject s." I will use ``maxim M is obligatory" to 
refer to M being obligatory for any arbitrary subject, which I will show to be equivalent to M being 
obligatory for a specific subject.}%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ prohibited{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}prohibited\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isachardoublequoteclose}\isanewline
\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ permissible{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}permissible\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}prohibited\ M\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{I will say that a maxim is permissible for a subject if it is not prohibited for that subject to 
will that maxim.%
}%
\begin{isamarkuptext}%
One problem with prior formalizations of the categorical imperative was that they didn't
prohibit contradictory obligations, partially because DDL itself allows contradictory obligations. 
Kant subscribes to the general, popular view that morality is supposed to guide action, so ought implies 
can\footnote{Kohl points out that this principle is referred to as 
Kant's dictum or Kant's law in the literature. \cite[footnote 1]{kohl}}. Kohl reconstructs his argument for the principle as 
follows: if the will cannot comply with the moral law, then the moral law has no prescriptive authority 
for the will \cite[703-4]{kohl}. This defeats the purpose of Kant's theory—to develop an unconditional, categorical imperative 
for rational agents. Ought implies can requires that obligations never contradict, because an agent 
can't perform contradictory actions. Therefore, any ethical theory that respects ought implies can, 
and Kantian ethics in particular, must not result in conflicting obligations.

Kant only briefly discusses contradictory obligations in \emph{Metaphysics of Morals}, where he argues that 
conflicting moral obligations are impossible under his theory \cite[V224]{metaphysicsintro}. Particularly, the categorical imperative generates 
``strict negative laws of omission", which cannot conflict by definition \cite[45]{timmerman}.\footnote{The 
kinds of obligations generated by the FUL are called ``perfect duties" which arise from ``contradictions 
in conception," or maxims that we cannot even concieve of universalizing. These duties are always negative 
and thus never conflict. Kant also presents ``imperfect duties," generated from ``contradictions in will,"
or maxims that we can concieve of universalizing but would never want to. These duties tend to be broader, 
such as ``improve oneself" or "help others," and are secondary to perfect duties. My project only analyzes 
perfect duties, as these are stronger than imperfect duties.}

@@

Generalization across people coheres with Kantian ethics—maxims are not person-specific.
Indeed, Velleman argues that, because reason is accessible to everyone identically, obligations apply 
to all people \cite[25]{velleman}. When Kant describes the categorical imperative as the objective 
principle of the will, he is referring to the fact that, as opposed to a subjective principle, the categorical
imperative applies to all rational agents equally $\cite[16]{groundwork}$.

@@

  Free variables:
    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False))
    c = ($\lambda x. \_$)($i_1$ := False)
    g = ($\lambda x. \_$)($i_1$ := False)
    s = $s_1$\color{black}
Recall that Nitpick is a model checker that finds models making certain formulae true or false. In this 
case, Nitpick finds a model satisfying the given formula (which simply requires that the sentence 
``s wills (c, a, g)'' is permissible but not obligator). This model consists of the above specifications 
of a, c, g, and s.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
I also expect that any arbitrary maxim should be either permissible or prohibited, since all 
acts are either permissible or prohibited.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ perm{\isacharunderscore}or{\isacharunderscore}prohibited{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}prohibited\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{by}\isamarkupfalse%
\ blast\isanewline
%
\isamarkupcmt{This simple test passes immediately by the definitions of  permissible and prohibited.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Obligation should be strictly stronger than permissibility. In other words, if a maxim is 
obligated at a world, it should be permissible at that world. Below I test this property.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ obligated{\isacharunderscore}then{\isacharunderscore}permissible{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O{\isacharbraceleft}W{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ {\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ w\ {\isachardoublequoteclose}\isanewline
%
\isadelimproof
\ \ %
\endisadelimproof
%
\isatagproof
\isacommand{using}\isamarkupfalse%
\ no{\isacharunderscore}contradictions\ \isacommand{by}\isamarkupfalse%
\ auto\isanewline
%
\isamarkupcmt{This test passes and Isabelle is able to find a proof for the fact that all obligatory maxims are 
also permissible.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
The above test failed under Kroy's formalization of the categorical imperative and is thus evidence 
that my formalization improves upon Kroy's. Interestingly, this new test passes because of the additional
added axiom that prohibits contradictory obligations (recall that Kroy's formalization allowed contradictory
obligations). The proof is clear: if maxims are either permissible or prohibited and obligation contradicts
prohibition, then obligation must result in permissibility. Moreover, this property REQUIRES that 
there be no contradictory obligations. Formally, in the base logic DDL, I can show the sentence 
$(O \{A\} \wedge O \{\neg A\}) \mathbf{\longrightarrow} (\neg (O \{A\} \mathbf{\longrightarrow}  P \{A\})) w$
\footnote{Sledgehammer can show this sentence to be true in DDL and in Kroy's formalization.}.
In English, if A and not A are obligated, then A can be obligated but not permissible.

Is there anything philosophically interesting here? Something about the possibility of genuine moral 
conflict?%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Next, I will test if the formalization allows for vacuous obligations or modal collapse. These 
tests are sanity checks confirmed that the obligation operator is doesn't collapse. First, I will check 
that any arbitrary term isn't obligated.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{lemma}\isamarkupfalse%
\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ c\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O{\isacharbraceleft}A{\isacharbar}c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
\ \ \isacommand{nitpick}\isamarkupfalse%
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
\isadelimproof
\ %
\endisadelimproof
%
\isatagproof
\isacommand{oops}\isamarkupfalse%
\isanewline
%
\isamarkupcmt{This test passes—Nitpick finds a model where A isn't obligated in circumstances c.
\color{blue} Nitpick found a counterexample for card i = 1 and card s = 2:

@@

@@

%:%308=245%:%
%:%309=246%:%
%:%310=247%:%
%:%311=248%:%
%:%312=249%:%
%:%313=250%:%

@@

%:%316=253%:%
%:%317=254%:%
%:%318=255%:%
%:%319=256%:%
%:%320=257%:%
%:%321=258%:%
%:%322=259%:%
%:%323=260%:%
%:%324=261%:%
%:%325=262%:%
%:%326=263%:%
%:%327=264%:%
%:%328=265%:%
%:%329=266%:%
%:%330=267%:%
%:%331=268%:%
%:%332=269%:%
%:%334=271%:%
%:%335=271%:%
%:%336=272%:%
%:%338=273%:%
%:%339=274%:%
%:%340=274%:%
%:%341=275%:%
%:%342=276%:%
%:%343=276%:%
%:%345=277%:%
%:%346=278%:%
%:%347=279%:%
%:%355=281%:%
%:%367=283%:%
%:%368=284%:%
%:%369=285%:%
%:%370=286%:%
%:%371=287%:%
%:%372=288%:%
%:%374=291%:%
%:%375=291%:%
%:%377=292%:%
%:%378=293%:%
%:%379=294%:%
%:%380=295%:%
%:%381=295%:%
%:%382=296%:%
%:%383=297%:%
%:%384=297%:%
%:%386=297%:%
%:%390=297%:%
%:%391=297%:%
%:%392=298%:%
%:%393=298%:%
%:%394=298%:%
%:%403=300%:%
%:%404=301%:%
%:%405=302%:%
%:%406=303%:%
%:%407=304%:%
%:%408=305%:%
%:%409=306%:%
%:%410=307%:%
%:%411=308%:%
%:%412=309%:%
%:%413=310%:%
%:%414=311%:%
%:%415=312%:%
%:%416=313%:%
%:%417=314%:%
%:%418=315%:%
%:%419=316%:%
%:%421=318%:%
%:%422=318%:%
%:%423=319%:%
%:%425=320%:%
%:%426=321%:%
%:%427=321%:%
%:%428=322%:%
%:%429=323%:%
%:%430=323%:%
%:%432=324%:%
%:%433=325%:%
%:%434=325%:%
%:%435=326%:%
%:%436=327%:%
%:%437=327%:%
%:%438=328%:%
%:%439=328%:%
%:%441=328%:%
%:%445=328%:%
%:%446=328%:%
%:%448=329%:%
%:%449=330%:%
%:%450=331%:%
%:%451=332%:%
%:%452=333%:%
%:%453=334%:%
%:%454=335%:%
%:%455=336%:%
%:%456=337%:%
%:%457=338%:%
%:%458=339%:%
%:%466=339%:%
%:%467=340%:%
%:%468=341%:%
%:%469=341%:%
%:%470=342%:%
%:%471=343%:%
%:%472=343%:%
%:%473=344%:%
%:%474=344%:%
%:%476=344%:%
%:%480=344%:%
%:%481=344%:%
%:%483=345%:%
%:%484=346%:%
%:%485=347%:%
%:%486=348%:%
%:%487=349%:%
%:%488=350%:%
%:%498=352%:%
%:%499=353%:%
%:%500=354%:%
%:%501=355%:%
%:%502=356%:%
%:%503=357%:%
%:%504=358%:%
%:%505=359%:%
%:%506=360%:%
%:%507=361%:%
%:%508=362%:%
%:%509=363%:%
%:%510=364%:%
%:%511=365%:%
%:%512=366%:%
%:%513=367%:%
%:%514=368%:%
%:%515=369%:%
%:%516=370%:%
%:%517=371%:%
%:%521=373%:%
%:%522=374%:%
%:%523=375%:%
%:%524=376%:%
%:%525=377%:%
%:%534=379%:%
%:%546=381%:%
%:%547=382%:%
%:%548=383%:%
%:%549=384%:%
%:%553=386%:%
%:%554=387%:%
%:%555=388%:%
%:%556=389%:%
%:%557=390%:%
%:%558=391%:%
%:%559=392%:%
%:%560=393%:%
%:%561=394%:%
%:%562=395%:%
%:%563=396%:%
%:%564=397%:%
%:%565=398%:%
%:%566=399%:%
%:%567=400%:%
%:%568=401%:%
%:%570=403%:%
%:%571=403%:%
%:%573=404%:%
%:%574=405%:%
%:%575=405%:%
%:%576=406%:%
%:%577=406%:%
%:%579=407%:%
%:%580=408%:%
%:%581=408%:%
%:%582=409%:%
%:%583=409%:%
%:%585=410%:%
%:%586=411%:%
%:%587=411%:%
%:%588=412%:%
%:%589=413%:%
%:%590=413%:%
%:%591=414%:%
%:%593=415%:%
%:%596=417%:%
%:%597=418%:%
%:%598=419%:%
%:%600=421%:%
%:%601=421%:%
%:%602=422%:%
%:%604=423%:%
%:%605=424%:%
%:%606=425%:%
%:%607=426%:%
%:%608=427%:%
%:%609=427%:%
%:%610=428%:%
%:%611=429%:%
%:%612=429%:%
%:%613=430%:%
%:%615=431%:%
%:%616=432%:%
%:%617=433%:%
%:%618=434%:%
%:%619=435%:%
%:%620=435%:%
%:%621=436%:%
%:%622=437%:%
%:%623=437%:%
%:%624=438%:%
%:%626=439%:%
%:%627=440%:%
%:%628=441%:%
%:%629=442%:%
%:%630=443%:%
%:%633=445%:%
%:%634=446%:%
%:%636=448%:%
%:%637=448%:%
%:%638=449%:%
%:%639=450%:%
%:%640=451%:%
%:%641=452%:%
%:%648=453%:%
%:%649=453%:%
%:%650=454%:%
%:%651=454%:%
%:%652=455%:%
%:%653=455%:%
%:%655=456%:%
%:%656=457%:%
%:%657=457%:%
%:%658=458%:%
%:%659=458%:%
%:%660=459%:%
%:%661=459%:%
%:%662=459%:%
%:%663=460%:%
%:%673=462%:%
%:%674=463%:%
%:%675=464%:%
%:%676=465%:%
%:%677=466%:%
%:%678=467%:%
%:%679=468%:%
%:%680=469%:%
%:%682=471%:%
%:%683=471%:%
%:%684=472%:%
%:%685=472%:%
%:%686=473%:%
%:%688=474%:%
%:%689=475%:%
%:%690=475%:%
%:%691=476%:%
%:%692=477%:%
%:%693=477%:%
%:%694=478%:%
%:%696=479%:%
%:%697=480%:%
%:%698=480%:%
%:%699=481%:%
%:%700=482%:%
%:%701=482%:%
%:%702=483%:%
%:%703=484%:%
%:%705=485%:%
%:%706=485%:%
%:%707=486%:%
%:%708=487%:%
%:%710=488%:%
%:%711=488%:%
%:%712=489%:%
%:%719=490%:%
%:%720=490%:%
%:%721=491%:%
%:%722=491%:%
%:%723=492%:%
%:%724=492%:%
%:%725=492%:%
%:%726=493%:%
%:%727=493%:%
%:%728=494%:%
%:%729=494%:%
%:%730=494%:%
%:%731=495%:%
%:%732=495%:%
%:%734=496%:%
%:%744=498%:%
%:%745=499%:%
%:%746=500%:%
%:%747=501%:%
%:%748=502%:%
%:%749=503%:%
%:%750=504%:%
%:%751=505%:%
%:%752=506%:%
%:%753=507%:%
%:%754=508%:%
%:%755=509%:%
%:%756=510%:%
%:%757=511%:%
%:%758=512%:%
%:%759=513%:%
%:%760=514%:%
%:%761=515%:%
%:%762=516%:%
%:%763=517%:%
%:%764=518%:%
%:%765=519%:%
%:%766=520%:%
%:%767=521%:%
%:%768=522%:%
%:%769=523%:%
%:%770=524%:%
%:%771=525%:%
%:%772=526%:%
%:%773=527%:%
%:%774=528%:%
%:%775=529%:%
%:%776=530%:%
%:%777=531%:%
%:%778=532%:%
%:%779=533%:%
%:%780=534%:%
%:%781=535%:%
%:%782=536%:%
%:%783=537%:%
%:%787=539%:%
%:%788=540%:%
%:%789=541%:%
%:%791=543%:%
%:%792=543%:%
%:%793=544%:%
%:%794=545%:%
%:%795=545%:%
%:%797=545%:%
%:%801=545%:%
%:%802=545%:%
%:%804=546%:%
%:%805=547%:%
%:%806=548%:%
%:%807=549%:%
%:%808=550%:%
%:%809=551%:%
%:%819=554%:%
%:%820=555%:%
%:%821=556%:%
%:%830=558%:%
%:%842=560%:%
%:%843=561%:%
%:%844=562%:%
%:%845=563%:%
%:%846=564%:%
%:%847=565%:%
%:%848=566%:%
%:%849=567%:%
%:%850=568%:%
%:%851=569%:%
%:%852=570%:%
%:%853=571%:%
%:%854=572%:%
%:%855=573%:%
%:%856=574%:%
%:%857=575%:%
%:%858=576%:%
%:%859=577%:%
%:%860=578%:%
%:%861=579%:%
%:%863=581%:%
%:%864=581%:%
%:%865=582%:%
%:%868=583%:%
%:%872=583%:%
%:%873=583%:%
%:%878=583%:%
%:%881=584%:%
%:%882=585%:%
%:%883=585%:%
%:%884=586%:%
%:%887=587%:%
%:%891=587%:%
%:%892=587%:%
%:%897=587%:%
%:%900=588%:%
%:%901=589%:%
%:%902=589%:%
%:%903=590%:%
%:%906=591%:%
%:%910=591%:%

>>>>

Notice that the antecedent specifies that the circumstances hold at the given world. 
When evaluating if a maxim is universalizable or not, we want to ignore worlds where the circumstance 
do not hold. At these worlds, the maxim is trivially effective and thus trivially universalizable. If we didn't exclude such worlds from 
consideration, a maxim with circumstances that ever fail to hold would be universalizable. Clearly 
this is not a desirable conclusion, since maxims like ``When you need money, lie to get easy money"
would be universalizable.%
As before, the concepts of prohibition and permissibility will be helpful here. The unit of 
evaluation for my formalization of the FUL is the act of willing a maxim, which entails performing 
the maxim's act in the relevant circumstances. Therefore, I will say that, just as the act of willing a
 maxim can be obligatory for a subject, it can be prohibited or permissible for a subject.\footnote{In 
the rest of this section, for convenience, I will use the phrase ``subject s willing maxim M is obligatory" 
interchangeably with ``maxim M is obligatory for subject s." I will use ``maxim M is obligatory" to 
refer to M being obligatory for any arbitrary subject, which I will show to be equivalent to M being 
obligatory for a specific subject.}%
\ prohibited{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}prohibited\ {\isasymequiv}\ {\isasymlambda}{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isachardot}\ O{\isacharbraceleft}\isactrlbold {\isasymnot}\ {\isacharparenleft}will\ {\isacharparenleft}c{\isacharcomma}a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ {\isacharbar}\ c{\isacharbraceright}{\isachardoublequoteclose}\isanewline
\ permissible{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}s{\isasymRightarrow}t{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}permissible\ {\isasymequiv}\ {\isasymlambda}M\ s{\isachardot}\ \isactrlbold {\isasymnot}\ {\isacharparenleft}prohibited\ M\ s{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{I will say that a maxim is permissible for a subject if it is not prohibited for that subject to 
will that maxim.%

@@

@@

    a = ($\lambda x. \_$)($s_1$ := ($\lambda x. \_$)($i_1$ := False))
    s = $s_1$\color{black}
Recall that Nitpick is a model checker that finds models making certain formulae true or false. In this 
case, Nitpick finds a model satisfying the given formula (which simply requires that the sentence 
``s wills (c, a, g)'' is permissible but not obligator). This model consists of the above specifications 
of a, c, g, and s.%
I also expect that any arbitrary maxim should be either permissible or prohibited, since all 
acts are either permissible or prohibited.%
\ perm{\isacharunderscore}or{\isacharunderscore}prohibited{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}{\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}\ \isactrlbold {\isasymor}\ {\isacharparenleft}prohibited\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ w{\isachardoublequoteclose}\isanewline
\isamarkupcmt{This simple test passes immediately by the definitions of  permissible and prohibited.%
Obligation should be strictly stronger than permissibility. In other words, if a maxim is 
obligated at a world, it should be permissible at that world. Below I test this property.%
\ obligated{\isacharunderscore}then{\isacharunderscore}permissible{\isacharcolon}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isacharparenleft}O{\isacharbraceleft}W{\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ s{\isacharbar}c{\isacharbraceright}\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}{\isacharparenleft}permissible\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}\ {\isacharparenright}\ s{\isacharparenright}{\isacharparenright}\ w\ {\isachardoublequoteclose}\isanewline
\isamarkupcmt{This test passes and Isabelle is able to find a proof for the fact that all obligatory maxims are 
also permissible.%
The above test failed under Kroy's formalization of the categorical imperative and is thus evidence 
that my formalization improves upon Kroy's. Interestingly, this new test passes because of the additional
added axiom that prohibits contradictory obligations (recall that Kroy's formalization allowed contradictory
obligations).%
Next, I will test if the formalization allows for vacuous obligations or modal collapse. These 
tests are sanity checks confirmed that the obligation operator is doesn't collapse. First, I will check 
that any arbitrary term isn't obligated.%
\ arbitrary{\isacharunderscore}obligations{\isacharcolon}\isanewline
\ \ \isakeyword{fixes}\ c\ A{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}O{\isacharbraceleft}A{\isacharbar}c{\isacharbraceright}\ w{\isachardoublequoteclose}\isanewline
\ {\isacharbrackleft}user{\isacharunderscore}axioms{\isacharequal}true{\isacharcomma}\ falsify{\isacharbrackright}%
\isamarkupcmt{This test passes—Nitpick finds a model where A isn't obligated in circumstances c.
\color{blue} Nitpick found a counterexample for card i = 1 and card s = 2:

@@

\ distribution{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}O\ {\isacharbraceleft}A{\isacharbraceright}\ \isactrlbold {\isasymand}\ O\ {\isacharbraceleft}B{\isacharbraceright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ O\ {\isacharbraceleft}A\ \isactrlbold {\isasymand}\ B{\isacharbraceright}{\isachardoublequoteclose}\isanewline

@@

%:%308=246%:%
%:%309=247%:%
%:%310=248%:%
%:%311=249%:%
%:%313=251%:%

@@

%:%317=253%:%
%:%318=254%:%
%:%319=254%:%
%:%320=255%:%
%:%321=256%:%
%:%322=256%:%
%:%324=257%:%
%:%325=258%:%
%:%326=259%:%
%:%334=261%:%
%:%346=263%:%
%:%347=264%:%
%:%348=265%:%
%:%349=266%:%
%:%350=267%:%
%:%351=268%:%
%:%353=271%:%
%:%354=271%:%
%:%356=272%:%
%:%357=273%:%
%:%358=274%:%
%:%359=275%:%
%:%360=275%:%
%:%361=276%:%
%:%362=277%:%
%:%363=277%:%
%:%365=277%:%
%:%369=277%:%
%:%370=277%:%
%:%371=278%:%
%:%372=278%:%
%:%373=278%:%
%:%382=280%:%
%:%383=281%:%
%:%384=282%:%
%:%385=283%:%
%:%386=284%:%
%:%387=285%:%
%:%388=286%:%
%:%389=287%:%
%:%390=288%:%
%:%391=289%:%
%:%392=290%:%
%:%393=291%:%
%:%394=292%:%
%:%395=293%:%
%:%396=294%:%
%:%397=295%:%
%:%398=296%:%
%:%400=298%:%
%:%401=298%:%
%:%402=299%:%
%:%404=300%:%
%:%405=301%:%
%:%406=301%:%
%:%407=302%:%
%:%408=303%:%
%:%409=303%:%
%:%411=304%:%
%:%412=305%:%
%:%413=305%:%
%:%414=306%:%
%:%415=307%:%
%:%416=307%:%
%:%417=308%:%
%:%418=308%:%
%:%420=308%:%
%:%424=308%:%
%:%425=308%:%
%:%427=309%:%
%:%428=310%:%
%:%429=311%:%
%:%430=312%:%
%:%431=313%:%
%:%432=314%:%
%:%433=315%:%
%:%434=316%:%
%:%435=317%:%
%:%436=318%:%
%:%437=319%:%
%:%445=319%:%
%:%446=320%:%
%:%447=321%:%
%:%448=321%:%
%:%449=322%:%
%:%450=323%:%
%:%451=323%:%
%:%452=324%:%
%:%453=324%:%
%:%455=324%:%
%:%459=324%:%
%:%460=324%:%
%:%462=325%:%
%:%463=326%:%
%:%464=327%:%
%:%465=328%:%
%:%466=329%:%
%:%467=330%:%
%:%477=332%:%
%:%478=333%:%
%:%479=334%:%
%:%480=335%:%
%:%481=336%:%
%:%482=337%:%
%:%483=338%:%
%:%484=339%:%
%:%485=340%:%
%:%486=341%:%
%:%487=342%:%
%:%488=343%:%
%:%489=344%:%
%:%490=345%:%
%:%491=346%:%
%:%492=347%:%
%:%493=348%:%
%:%494=349%:%
%:%495=350%:%
%:%496=351%:%
%:%500=353%:%
%:%501=354%:%
%:%502=355%:%
%:%503=356%:%
%:%504=357%:%
%:%513=359%:%
%:%525=361%:%
%:%526=362%:%
%:%527=363%:%
%:%528=364%:%
%:%532=366%:%
%:%533=367%:%
%:%534=368%:%
%:%535=369%:%
%:%536=370%:%
%:%537=371%:%
%:%538=372%:%
%:%539=373%:%
%:%540=374%:%
%:%541=375%:%
%:%542=376%:%
%:%543=377%:%
%:%544=378%:%
%:%545=379%:%
%:%546=380%:%
%:%547=381%:%
%:%549=383%:%
%:%550=383%:%
%:%552=384%:%
%:%553=385%:%
%:%554=385%:%
%:%555=386%:%
%:%556=386%:%
%:%558=387%:%
%:%559=388%:%
%:%560=388%:%
%:%561=389%:%
%:%562=389%:%
%:%564=390%:%
%:%565=391%:%
%:%566=391%:%
%:%567=392%:%
%:%568=393%:%
%:%569=393%:%
%:%570=394%:%
%:%572=395%:%
%:%575=397%:%
%:%576=398%:%
%:%577=399%:%
%:%579=401%:%
%:%580=401%:%
%:%581=402%:%
%:%583=403%:%
%:%584=404%:%
%:%585=405%:%
%:%586=406%:%
%:%587=407%:%
%:%588=407%:%
%:%589=408%:%
%:%590=409%:%
%:%591=409%:%
%:%592=410%:%
%:%594=411%:%
%:%595=412%:%
%:%596=413%:%
%:%597=414%:%
%:%598=415%:%
%:%599=415%:%
%:%600=416%:%
%:%601=417%:%
%:%602=417%:%
%:%603=418%:%
%:%605=419%:%
%:%606=420%:%
%:%607=421%:%
%:%608=422%:%
%:%609=423%:%
%:%612=425%:%
%:%613=426%:%
%:%615=428%:%
%:%616=428%:%
%:%617=429%:%
%:%618=430%:%
%:%619=431%:%
%:%620=432%:%
%:%627=433%:%
%:%628=433%:%
%:%629=434%:%
%:%630=434%:%
%:%631=435%:%
%:%632=435%:%
%:%634=436%:%
%:%635=437%:%
%:%636=437%:%
%:%637=438%:%
%:%638=438%:%
%:%639=439%:%
%:%640=439%:%
%:%641=439%:%
%:%642=440%:%
%:%652=442%:%
%:%653=443%:%
%:%654=444%:%
%:%655=445%:%
%:%656=446%:%
%:%657=447%:%
%:%658=448%:%
%:%659=449%:%
%:%661=451%:%
%:%662=451%:%
%:%663=452%:%
%:%664=452%:%
%:%665=453%:%
%:%667=454%:%
%:%668=455%:%
%:%669=455%:%
%:%670=456%:%
%:%671=457%:%
%:%672=457%:%
%:%673=458%:%
%:%675=459%:%
%:%676=460%:%
%:%677=460%:%
%:%678=461%:%
%:%679=462%:%
%:%680=462%:%
%:%681=463%:%
%:%682=464%:%
%:%684=465%:%
%:%685=465%:%
%:%686=466%:%
%:%687=467%:%
%:%689=468%:%
%:%690=468%:%
%:%691=469%:%
%:%698=470%:%
%:%699=470%:%
%:%700=471%:%
%:%701=471%:%
%:%702=472%:%
%:%703=472%:%
%:%704=472%:%
%:%705=473%:%
%:%706=473%:%
%:%707=474%:%
%:%708=474%:%
%:%709=474%:%
%:%710=475%:%
%:%711=475%:%
%:%713=476%:%
%:%723=478%:%
%:%724=479%:%
%:%725=480%:%
%:%726=481%:%
%:%727=482%:%
%:%728=483%:%
%:%729=484%:%
%:%730=485%:%
%:%731=486%:%
%:%732=487%:%
%:%733=488%:%
%:%734=489%:%
%:%735=490%:%
%:%736=491%:%
%:%737=492%:%
%:%738=493%:%
%:%739=494%:%
%:%740=495%:%
%:%741=496%:%
%:%742=497%:%
%:%743=498%:%
%:%744=499%:%
%:%745=500%:%
%:%746=501%:%
%:%747=502%:%
%:%748=503%:%
%:%749=504%:%
%:%750=505%:%
%:%751=506%:%
%:%752=507%:%
%:%753=508%:%
%:%754=509%:%
%:%755=510%:%
%:%756=511%:%
%:%757=512%:%
%:%758=513%:%
%:%759=514%:%
%:%760=515%:%
%:%761=516%:%
%:%762=517%:%
%:%766=519%:%
%:%767=520%:%
%:%768=521%:%
%:%770=523%:%
%:%771=523%:%
%:%772=524%:%
%:%773=525%:%
%:%774=525%:%
%:%776=525%:%
%:%780=525%:%
%:%781=525%:%
%:%783=526%:%
%:%784=527%:%
%:%785=528%:%
%:%786=529%:%
%:%787=530%:%
%:%788=531%:%
%:%798=534%:%
%:%799=535%:%
%:%800=536%:%
%:%809=538%:%
%:%821=540%:%
%:%822=541%:%
%:%823=542%:%
%:%824=543%:%
%:%825=544%:%
%:%826=545%:%
%:%827=546%:%
%:%828=547%:%
%:%829=548%:%
%:%830=549%:%
%:%831=550%:%
%:%832=551%:%
%:%833=552%:%
%:%834=553%:%
%:%836=555%:%
%:%837=555%:%
%:%838=556%:%
%:%841=557%:%
%:%845=557%:%
%:%846=557%:%
%:%851=557%:%
%:%854=558%:%
%:%855=559%:%
%:%856=559%:%
%:%857=560%:%
%:%860=561%:%
%:%864=561%:%
%:%865=561%:%
%:%870=561%:%
%:%873=562%:%
%:%874=563%:%
%:%875=563%:%
%:%876=564%:%
%:%879=565%:%
%:%883=565%:%
%:%884=565%:%
%:%889=565%:%
%:%892=566%:%
%:%893=567%:%
%:%894=567%:%
%:%895=568%:%
%:%898=569%:%
%:%902=569%:%
%:%903=569%:%
%:%912=571%:%
%:%913=572%:%
%:%914=573%:%
%:%915=574%:%
%:%916=575%:%
%:%917=576%:%
%:%918=577%:%
%:%920=579%:%
%:%921=579%:%
%:%922=580%:%
%:%923=581%:%
%:%924=581%:%
%:%926=581%:%
%:%930=581%:%
%:%931=581%:%
%:%933=582%:%
%:%934=583%:%
%:%935=584%:%
